Assigning Scouts to Optimal Patrols

### 2016-05-25 draft1.tex
More edits
Added "Data" section and "Appendix B" talking about Stirling number.
Updated Conclusion section.

@@

\begin{table}[h]
	\caption{}\label{eqtable}
	\renewcommand\arraystretch{1.5}
	\noindent\[
	\begin{array}{|c|c|}
	\hline
	\textbf{Patrol 1}&\textbf{Patrol 2}\\
	\hline
	\text{Brandon, Cameron, Colby,}&\text{Christian, Daniel, Jake,}\\
	\text{Darwin, Evan, Tommy}&\text{Jordan, Nathan, Patrick, Timmy}\\
	\hline
	\end{array}
	\]
\end{table}
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.60]{graph}
\end{figure}

@@

@@

>>>>

\section*{Data}
The 13 different recruited scouts are Brandon, Cameron, Christian, Colby, Daniel, Darwin, Evan, Jake, Jordan, Nathan, Patrick, Timmy and Tommy. After the Scoutmaster collected the likes and dislikes of each scout, he presented the data as follows: 
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.60]{graph}
\end{figure}

The solid arrow represents a preferred companion. For example, there is a solid arrow from Tommy pointing to Colby indicating that Tommy likes to be with Colby. A dashed arrow represents a dislike. For example, there is a dashed arrow from Tommy to Jordan showing that Tommy does not want to be with Jordan. Furthermore, the Scoutmaster provided us a separate email, and indicated that Colby and Jordan cannot be in the same troop. The highlighted arrows in the figure above does not mean anything new between the relationships of the boy scouts.

The Stirling number of the second kind provides the total possible ways to arrange any number of distinguishable objects to indistinguishable groups as long as any troop size is permitted and no possible empty troops. For the data in this project, the Stirling number of the second kind for 13 scouts into 2 troops is 4095. This number provides an upper bound on the possible arrangements for the specific problem tackled in this project.

@@

\begin{table}[h]
	\caption{}\label{eqtable}
	\renewcommand\arraystretch{1.5}
	\noindent\[
	\begin{array}{|c|c|}
	\hline
	\textbf{Patrol 1}&\textbf{Patrol 2}\\
	\hline
	\text{Brandon, Cameron, Colby,}&\text{Christian, Daniel, Jake,}\\
	\text{Darwin, Evan, Tommy}&\text{Jordan, Nathan, Patrick, Timmy}\\
	\hline
	\end{array}
	\]
\end{table}

@@

\section*{Appendix B}
The solution for finding the Stirling number of the second kinds for $n = 13$ scouts to be arranged in $k = 2$ troops:
\begin{gather*}
	S(n,k) = \frac{1}{k!} \sum_{i=0}^{k}(-1)^k {2 \choose i} (k - i)^{n} \\
	S(13,2) = \frac{1}{2!} \sum_{i=0}^{2}(-1)^2 {2 \choose i} (2 - i)^{13} \\
	S(13, 2) = 4095
\end{gather*}

@@

\section*{Conclusions}
We initially struggled deciding on an appropriate objective function to partition the scouts to different groups. Follow up interviews with Scoutmaster Gene Bruce allowed us to decide on this function. We relied on his expertise and intuition rather than trying to blindly decide on which types of relationships should be fostered and avoided to determine our objective function. Thus, we learned necessary communication skills and consideration of our community partner's needs.

With a feasibility check of how many solutions possible once the mathematical model was decided using graphs, a brute force strategy was the most reliable method to arrive at a solution. Thus we were able to develop a program that can partition scouts using this strategy. We learned to utilize tools we have at hand. Further consideration of other methods later on to reduce the computational time of our algorithm.

\section*{Acknowledgments}
We would like to thank Scoutmaster Gene Bruce for providing us the necessary data and being extremely patient and understanding when discussing the background and problem. We would also like to thank Professor Sara Billey for the mentorship and guidance she provided throughout this project, and our TA Austin Tran for his comments and suggestions.
